---
title: "Network Vis"
author: "Rafael Cruz Gil"
date: "26 May 2018"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(igraph)
library(visNetwork)

```

## Network Visualisation

This visualisation presents the coin finds in 5 archaeological sites in Northen Israel. Yellow nodes represent mints where coins were made, gray nodes represent some of the 5 sites where the coins were found, but none were minted, and red nodes represent sites that both are a location of finds and had a mint. Hovering over each node will tell the name of the city.

```{r, map}

library(visNetwork)

nodes <- read_csv("nodes.csv")

links <- read_csv("edges.csv")

nodes$shape <- "dot"  
nodes$shadow <- TRUE 
nodes$title <- nodes$city 
nodes$label <- nodes$type.label 
nodes$size <- 25
nodes$borderWidth <- 2 
nodes$color.background <- c("slategrey", "gold", "tomato")[nodes$type]
nodes$color.highlight.background <- "orange"
nodes$color.highlight.border <- "darkred"
nodes$color.border <- "black"




visNetwork(nodes, links)  %>%
  visOptions(selectedBy = "label", 
             highlightNearest = TRUE) %>%
  visPhysics(stabilization = FALSE)

```